A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-19 rmtw/a6/latex8.tex
change structure of intro
Intro v1.more_or_less_done

\section{Introduction}
%API Design
An API is an interface defined in a programming language (in code) which can be accessed programatically by other software. (!!!Re-word this sentence a bit) %Add some more filler stuff here

%Software Evolution 
In the discipline of Software Evolution, such updates to applications are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive \cite{lientz1980software}. %explain these factors a bit more closely in the related work?

%Gap in Literature
There are no existing studies which analyse the motives behind API modifications using accepted Software Evolution theories. Studies that explore the intent behind API modifications exist \cite{hou2011exploring}, but only APIs to programming languages have been studied before.  %%add the 2nd paper that hou2011exploring intent linked to (john mentioned this) to above cite /// also add the honey language or whatever... john said "or is this a language" and googled it

%Problem statement
There is consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it may will the users of the API to update the code that is accessing the API. (!!!re-word) The most common reason for modifying an API after it has been deployed (!!! word?) is refactoring \cite{dig2005role} \cite{xing2006refactoring}. %refactoring isn't the reason... it's the process. look up why refactoring is done or change wording.

%Motivation
Because of the negative implications that modifications to to APIs cause for the API users, it is important to understand why changes to APIs happen. If most common pitfalls are known before the development of new APIs are know, these mistakes can mitigated.

@@

\subsection{Architecture / Reverse Engineering (or tracing previously made decisions)}

>>>>

\section{Introduction}
%API Design (and a little bit of ecosystems, and a bit of problem statement)
An API is an interface defined in a programming language (in code) which can be accessed programatically by other software. (!!!Re-word this sentence a bit) There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API (!!!re-word), and thus cause a disruption in the software ecosystem \cite{messerschmitt2005software} that the API's platform is a part of. Most commonly, already deployed APIs are modified due to code refactoring being made. \cite{dig2005role} \cite{xing2006refactoring}. 
%Software Evolution 
In the discipline of Software Evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.

%Gap in Literature
Existing studies that explore the intent behind API modifications exist \cite{hou2011exploring}. There are however no studies that attempt to map the motives behind changes to business needs or existing software evolution theories such as the four categories of maintenance \cite{lientz1980software}. The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}. No studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.

%Purpose (and a bit of problem statement)
Because of the negative implications that modifications to to APIs cause for the API users, it is important to understand why changes to APIs happen. If most common pitfalls are known before the development of new APIs are known, these mistakes can mitigated. Before the industry can make use of this information, the proposed common pitfalls must also be validated.

@@
